---
title: "Experiment 2 analyses and plots"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Setup: load data, define variables, etc

```{r load-data-define-variables}

rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

qc_filter <- T

no_first_rep_filter <- T

plot_normality     <- T
plot_fits_near_far <- F

source('./scripts/utils/load_transform_data_expt2.R')

qc_table <- import('./results/experiment2/qc_check_sheets/qc_table.csv')

if (qc_filter){
        
        qc_pass_ptp <- qc_table %>%
                filter(!qc_fail_overall) %>%
                select(ptp) %>% .[[1]]
        
        
        data_summary <- data_summary %>%
                filter(ptp %in% qc_pass_ptp)
        long_data <- long_data %>%
                filter(ptp %in% qc_pass_ptp) 
        mean_by_rep_long_all_types <- mean_by_rep_long_all_types %>%
                filter(ptp %in% qc_pass_ptp)
        
}

if (no_first_rep_filter){
        
        ptp_without_first_rep <- data_summary %>%
                group_by(ptp) %>%
                summarise(no_data_first_rep = any(no_data_first_rep)) %>%
                filter(no_data_first_rep) %>% 
                ungroup() %>%
                droplevels() %>%
                select(ptp) %>% .[[1]]
        
        data_summary <- data_summary %>%
                filter(!ptp %in% ptp_without_first_rep)
        long_data <- long_data %>%
                filter(!ptp %in% ptp_without_first_rep) 
        mean_by_rep_long_all_types <- mean_by_rep_long_all_types %>%
                filter(!ptp %in% ptp_without_first_rep)        
        
}

## BF test against 0 
reportBF = function(x, digits = 4){
        round(as.numeric(as.vector(x)), digits)
}


```


# Learning across all trials 

```{r learning-fits-across-participants-all-conditions, fig.height=4, fig.width=5}

# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'near_far_combined',
               ) %>%
        droplevels() %>%                
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T),
                  mouse_error_sd_across_ptp   = sd(mouse_error_mean, na.rm = T),
                  sem                         = mouse_error_sd_across_ptp/sqrt(n),
                  upper_95_ci = mouse_error_mean_across_ptp + qt(0.975,df = n-1)*sem,
                  lower_95_ci = mouse_error_mean_across_ptp - qt(0.975,df = n-1)*sem) %>% 
        ungroup() %>% 
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition)) +
        geom_point(size=1.5) +
        geom_line(size=0.5) +
        ggtitle('Learning Curves') +
        xlab('Image repetition') +
        ylab('Error') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,200,25)) +  
        coord_cartesian(ylim = c(0,200)) +
        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
        theme(plot.title = element_text(hjust = 0.5)) +
        scale_color_discrete(labels = c('Schema-2-2',
                                        'Schema-4-2',
                                        'Schema-4-4',
                                        'Schema-6-0'),
                             name = 'Condition')



print(fig_each_ptp)

ggsave(filename = 'learning_rates_all_cond.png', plot = fig_each_ptp, path = './results/experiment2/plots/', width = 5, height = 3, device='png', dpi=300)


```


# Block 2 error analyses:

## All PAs:

### Figure 6-B: Block 2 mean performance:


```{r block-2-overall, fig.width=6, fig.height=5}

# Barplot
p <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=block_2_mouse_error_mean,
                   fill=condition)) +
        geom_bar(stat = 'summary', 
                 fun = 'mean',
                 width = 0.8) +
        geom_violin(width = 0.7) +
        geom_boxplot(width = 0.15,
                     fatten = 4,
                     outlier.shape = '') + 
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.2) +
        ylab('Mean Block 2 Error') +
        xlab('') +
        theme(legend.position = '') + 
        scale_x_discrete(labels = c('Schema-2-2',
                                    'Schema-4-2',
                                    'Schema-4-4',
                                    'Schema-6-0')) +
        ggtitle('Mean Block 2 Accuracy') + 
        theme(plot.title = element_text(hjust = 0.5))
        
print(p) 

ggsave(filename = 'block_2_barplot.png', plot = p, path = './results/experiment2/plots/', width = 5, height = 3, device='png', dpi=300)

```

### Bayes Factors between pairs of conditions

```{r bf-analysis-pairs}

null_interval <- c(-Inf,Inf)

data_summary_wide_condition <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean_LOG)

data_summary_long_condition_differences <- data_summary_wide_condition %>%
        mutate(schema_2_2_min_4_2 = schema_2_2 - schema_4_2,
               schema_4_2_min_4_4 = schema_4_2 - schema_4_4,
               schema_2_2_min_6_0 = schema_2_2 - schema_6_0,
               schema_4_2_min_6_0 = schema_4_2 - schema_6_0,
               schema_4_4_min_6_0 = schema_4_4 - schema_6_0) %>%
        pivot_longer(cols = contains("_min_"),
                     names_to = "comparison",
                     values_to = "difference") %>%
        select(-starts_with("schema_"))

# For each do the BF test
bf_table_block_2_near_far_combined_condition_diff <- data_summary_long_condition_differences %>%
        group_by(comparison) %>%
        summarise(bf_10 = reportBF(ttestBF(cur_data()$difference,
                                        nullInterval = null_interval)[1],4),
                  bf_01 = 1/bf_10)


```

### Effect sizes between pairs of conditions

```{r effect-size-block-2-conditions}

idf <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        select(ptp,condition,block_2_mouse_error_mean_LOG)

es_table_block_2_near_far_combined_condition_diff <- idf %>%
        cohens_d(block_2_mouse_error_mean_LOG ~ condition, 
                 paired = TRUE, 
                 var.equal = FALSE,
                 hedges.correction = FALSE)


```

## Near vs Far PAs:

### Figure 6-C: Near vs Far for all conditions

```{r near-far-block-2-all-conditions, fig.width=5, fig.height=2}

# Barplot
p <- data_summary %>%
        filter(hidden_pa_img_type %in% c('near','far')) %>%
        droplevels() %>%
        ggplot(aes(x=hidden_pa_img_type,
                   y=block_2_mouse_error_mean,
                   fill=condition)) +
        geom_bar(stat = 'summary', 
                 fun = 'mean',
                 width = 0.8) +
        geom_violin(width = 0.7) +
        geom_boxplot(width = 0.15,
                     fatten = 4,
                     outlier.shape = '') +
        geom_point(alpha = 0.2) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +        
        ylab('Mean Block 2 Error') +
        xlab('') +
        facet_wrap(~condition, nrow = 1) +        
        theme(legend.position = '') +
        ggtitle('Near vs Far Hidden-PAs') +
        theme(plot.title = element_text(hjust = 0.5)) +
        scale_x_discrete(labels = c('Far','Near'))
        
print(p) 

ggsave(filename = 'near_far_barplot.png', plot = p, path = './results/experiment2/plots/', width = 10, height = 3, device='png', dpi=300)

```

### Figure 6-C: Bayes Factors near-far

```{r bf-near-far-all-conditions}

null_interval <- c(-Inf,0)


data_summary_wide_near_far <- data_summary %>%
        filter(hidden_pa_img_type %in% c('near','far')) %>% 
        droplevels() %>%
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = block_2_mouse_error_mean_LOG) %>% 
        mutate(near_minus_far = near-far)

# For each condition do the BF test
bf_table_block_2_near_far_diff <-
data_summary_wide_near_far %>%
        group_by(condition) %>%
        summarise(bf_10 = reportBF(ttestBF(cur_data()$near_minus_far,
                                        nullInterval = null_interval)[1],4),
                  bf_01 = 1/bf_10)

```

### Figure 6-C: Effect sizes near-far:

```{r effect-size-near-far-all-conditions}


idf <- data_summary %>%
        filter(hidden_pa_img_type %in% c('near','far')) %>% 
        droplevels() %>% 
        select(ptp, condition, hidden_pa_img_type, block_2_mouse_error_mean_LOG)

es_table_block_2_near_far_diff <- idf %>%
        group_by(condition) %>%
        cohens_d(block_2_mouse_error_mean_LOG ~ hidden_pa_img_type, 
        paired = TRUE, 
        var.equal = FALSE,
        hedges.correction = FALSE)

```

# Suppl Figure 10: Learning Rate Analysis


## Near and Far combined

```{r}

# Barplot
p <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=learning_rate_two_param_no_outlier,
                   fill=condition)) +
        geom_bar(stat = 'summary', 
                 fun = 'mean',
                 width = 0.8) +
        geom_violin(width = 0.5) +
        geom_boxplot(width = 0.15,
                     fatten = 4,
                     outlier.shape = '') + 
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.2) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        ylab('Learning Rate') +
        xlab('') +
        theme(legend.position = '') + 
        scale_x_discrete(labels = c('Schema-2-2',
                                    'Schema-4-2',
                                    'Schema-4-4',
                                    'Schema-6-0')) +
        ggtitle('Learning Rates') + 
        theme(plot.title = element_text(hjust = 0.5))
        
print(p) 

ggsave(filename = 'learning_rates_all_cond.png', plot = p, path = './results/experiment2/plots/', width = 4, height = 3, device='png', dpi=300)
```

### Bayes Factors: between pairs of conditions

```{r lr2-bf-analysis-pairs}

null_interval <- c(-Inf,Inf)

data_summary_lr2_wide_condition <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = learning_rate_two_param_no_outlier_G)

data_summary_lr2_long_condition_differences <- data_summary_lr2_wide_condition %>%
        mutate(schema_2_2_min_4_2 = schema_2_2 - schema_4_2,
               schema_4_2_min_4_4 = schema_4_2 - schema_4_4,
               schema_2_2_min_6_0 = schema_2_2 - schema_6_0,
               schema_4_2_min_6_0 = schema_4_2 - schema_6_0,
               schema_4_4_min_6_0 = schema_4_4 - schema_6_0) %>%
        pivot_longer(cols = contains("_min_"),
                     names_to = "comparison",
                     values_to = "difference") %>%
        select(-starts_with("schema_"))
        

# For each do the BF test
bf_table_lr2_near_far_combined_condition_diff <- data_summary_lr2_long_condition_differences %>%
        group_by(comparison) %>%
        summarise(bf_10 = reportBF(ttestBF(cur_data()$difference,
                                        nullInterval = null_interval)[1],4),
                  bf_01 = 1/bf_10)

```


### Effect sizes between pairs of conditions


```{r lr2-effect-sizes}

idf <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        select(ptp,condition,learning_rate_two_param_no_outlier_G)

es_table_lr2_near_far_combined_condition_diff <- idf %>%
        cohens_d(learning_rate_two_param_no_outlier_G ~ condition, 
                 paired = TRUE, 
                 var.equal = FALSE,
                 hedges.correction = FALSE)

```


# Suppl Figure 11: Block 1 and 2 error combined

```{r both-block-performance}

# Barplot
p <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=block_1_2_mouse_error_mean,
                   fill=condition)) +
        geom_bar(stat = 'summary', 
                 fun = 'mean',
                 width = 0.8) +
        geom_violin(width = 0.7) +
        geom_boxplot(width = 0.15,
                     fatten = 4,
                     outlier.shape = '') + 
        geom_jitter(width = 0.05,
                    height = 0,
                    alpha = 0.2) +
        ylab('Mean Block 1-2 Error') +
        xlab('') +
        theme(legend.position = '') + 
        scale_x_discrete(labels = c('Schema-2-2',
                                    'Schema-4-2',
                                    'Schema-4-4',
                                    'Schema-6-0')) +
        ggtitle('Mean Block 1-2 Accuracy') + 
        theme(plot.title = element_text(hjust = 0.5))
        
print(p) 

ggsave(filename = 'block_1_2_barplot.png', plot = p, path = './results/experiment2/plots/', width = 5, height = 3, device='png', dpi=300)

```

## Bayes Factors: between pairs of conditions

```{r bf-block-1-2-combined}


null_interval <- c(-Inf,Inf)

data_summary_blocks_1_2_wide_condition <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_1_2_mouse_error_mean_LOG)

data_summary_blocks_1_2_long_condition_differences <- data_summary_blocks_1_2_wide_condition %>%
        mutate(schema_2_2_min_4_2 = schema_2_2 - schema_4_2,
               schema_4_2_min_4_4 = schema_4_2 - schema_4_4,
               schema_2_2_min_6_0 = schema_2_2 - schema_6_0,
               schema_4_2_min_6_0 = schema_4_2 - schema_6_0,
               schema_4_4_min_6_0 = schema_4_4 - schema_6_0) %>%
        pivot_longer(cols = contains("_min_"),
                     names_to = "comparison",
                     values_to = "difference") %>%
        select(-starts_with("schema_"))
        

# For each do the BF test
bf_table_blocks_1_2_near_far_combined_condition_diff <- data_summary_blocks_1_2_long_condition_differences %>%
        group_by(comparison) %>%
        summarise(bf_10 = reportBF(ttestBF(cur_data()$difference,
                                        nullInterval = null_interval)[1],4),
                  bf_01 = 1/bf_10)

```

## Effect sizes between pairs of conditions

```{r effect-size-combined-block-1-2}

idf <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        select(ptp,condition,block_1_2_mouse_error_mean_LOG)

es_table_blocks_1_2_near_far_combined_condition_diff <- idf %>%
        cohens_d(block_1_2_mouse_error_mean_LOG ~ condition, 
                 paired = TRUE, 
                 var.equal = FALSE,
                 hedges.correction = FALSE)

```


